---
title: "Creating Graphs with ggplot2"
author: "Connor"
date: "1/27/2020"
output: html_document
---

# Plots with ggplot2

We are going to make plots in R using the ggplot2 package from the tidyverse

```{r setup, message=FALSE}

library(tidyverse)
library(here) # install.packages("here")
library(readxl) # install.packages("readxl")

```

# California National Parks Data

```{r read data}
ca_np <- read_csv(here("data/ca_np.csv"))
ci_np <- read_xlsx("data/ci_np.xlsx")

names(ci_np)
```


```{r line plot}
ggplot(data = ci_np, aes(x = year, y = visitors)) + geom_line()
```


```{r base layer}
gg_base <- (ggplot(data = ci_np, aes(x = year, y = visitors)))

```

### Customization Notes

- Line/Point colors: color
- Change line type: linetype
- Change point style: pch
- Change transparency: alpha

```{r customization start}
gg_base + geom_line(
  color = "purple", 
  alpha = .7,
  linetype = "dashed")
```


```{r}
gg_base + geom_point(
 pch = 17,
 size = 2.5,
 color = "blue")

```

```{r}
gg_base +
  geom_point(
    aes(size = visitors, color = year),
    pch = 17)
```

### Use gg-themes for overall updates
- theme_light()
- theme_minimal()
- theme_bw()
```{r theme}
gg_base +
  geom_area() +
  theme_light()
```

### Create a multi-series line plot using data for all CA National Parks

```{r}
gg_total <- ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name))
gg_total + geom_line(
  aes(color = park_name )
)
```
```{r}
np_graph <- (ggplot( data = ca_np, aes(x = year, y = visitors)) + geom_point(aes(color = park_name), show.legend = FALSE) +
  facet_wrap(~park_name, scales = "free") +
  theme_minimal())
view(np_graph)
```
### Export my graph as a .png

```{r}
ggsave(plot = np_graph, here("figures", "np_graph.png"))

```


